TBD

### 2023-05-17 final/paper/main.tex

\author{Hsieh Cheng-Han, Hsu Ting-Hao, Sun Shih-Yu, Lu Che-Yuan, Huang Chia-Yen}
\date{June 2023}
\maketitle

@@

@@

\section{Experiment result}
  \begin{table*}[htb]
    \newcommand{\z}{\phantom{0}}
    \caption{\textsc{Comparison of Classification Techniques.}}
      \vspace{-\baselineskip}
    \begin{tabular}{@{}lccccccl@{}}\toprule
    Technique & Search (s)       & testA                              & testA-normalized             & testB                          & testB-normalized \\ \midrule
    KNN-Brute-Force  & $0.009$   & $76.6169 \pm \z{0}$                & $\bf{80.597 \pm 0}$          & $78 \pm \z{0}$                 & $\bf{80 \pm \z{0}}$\\
    KNN-ANNOY-DFS    & $0.003$   & $75.2438 \pm \z{1.8762}$           & $76.1294 \pm 2.0977$         & $74.9 \pm \z{2.5554}$          & $76.4 \pm \z{2.5377}$\\
    KNN-ANNOY-BFS    & $0.012$   & $76.6567 \pm \z{0.5340}$           & $\bf{80.597 \pm 0}$          & $\bf{78.16 \pm \z{0.7310}}$    & $\bf{80 \pm \z{0}}$\\
    decision tree    & $0.009$   & $74.1294 \pm \z{0}$                & $74.1294 \pm 0$              & $76 \pm \z{0}$                 & $77 \pm \z{0}$\\
    random forest    & $0.004$   & $78.6965 \pm \z{1.7510}$           & $78.5373 \pm 1.452$          & $77.98 \pm \z{2.083}$          & $77.5 \pm \z{2.516}$\\
    SVM-GA           & $1.846$   & $76.6616 \pm \z{4.0301}$           & $75.9219 \pm 2.736$          & $75 \pm \z{2}$                 & $75 \pm \z{4}$\\
    Neural Network   & $3.2$     & $\bf{81.7910 \pm \z{2.0294}}$      & $80.2985 \pm 1.4106$         & $78 \pm \z{1.6733}$            & $77.5 \pm \z{1.892}$\\
    Naive Bayes classifier-GA  & $14.29$ & $78.5353 \pm \z{0.0322}$   & $72.6866 \pm 0.0237$         & $77.4038 \pm \z{0.0626}$       & $71 \pm \z{0.0289}$\\
    PLA-pocket       & $0.00052$ & $63.682 \pm \z{0}$                 & $3.162 \pm 0$                & $63 \pm \z{0}$                 & $3.162 \pm \z{0}$\\ \midrule
    \end{tabular}
    \label{table:overall}
      \vspace{-\baselineskip}
  \end{table*}

>>>>

\author{Hsieh Cheng-Han, Hsu Ting-Hao, Sun Shih-Yu, Lu Che-Yuan, Huang Chia-Yen}
\date{May 2023}
\maketitle

@@

\subsection*{Data preprocess}

\bf{Autoencoder (AE)}: \rm{Autoencoder}

\bf{Principal components analysis (PCA)}: \rm{Principal components analysis}

\subsection*{Classification algorithm}

\bf{k-nearest neighbors (KNN) classification algorithm}: \rm{The} KNN classification algorithm is a supervised learning 
method which is first developed by Fix and Hodges \cite{10.2307/1403797}. The idea of KNN is based on the idiom, 
"birds of a feather flock together". By picking the $k$-nearest neighbors of a data point, the unkonwn class label 
can be determined. Lots of works \cite{6528591} \cite{8276012} \cite{vijayan2014study} show the fact that KNN performs  
well for prediction of diabetes disease.

\bf{support vector machine (SVM)}: \rm{Given} a set of training datas, where each data is labeled as a binary class, such as 
$0$ and $1$, SVM training algorithm creates a model that assigns new examples to the binay labels by making it a non-probabilistic 
binary linear classifier. In addition, accroding to \cite{amari1999improving} \cite{hofmann2006support}, SVM can also use a 
method called kernel trick to effectively perform non-linear classification by implicitly mapping its inputs into a high-dimensional 
feature space.

\bf{neural network}: \rm{Neural} network have been used in many fields to deal with intricate datas. With input layer, hidden 
layer and output layer constructed by neurons, each data in dataset is processed while passing through neurons, layer by layer. 
After the processing, the outcome can be used to predict.Using back propogation, the accuracy of predictions increase in each 
training. In order to construct the hidden layer more efficient, NAS(Neural Arcitecture Searching) is used to search suitable 
structure for hidden layer, increasing the accuracy.According to \cite{Gadekallu2020}\cite{Beghriche2021}, many neural network 
have been constructed and trained already, with high efficiency and accuracy in prediction of diabetes.

\subsection*{Clustering algorithm}

\bf{DBSCAN}: \rm{DBSCAN}

\bf{kmeans}: \rm{kmeans}

@@

\section{Experiment result}
  \begin{table*}[htb]
    \newcommand{\z}{\phantom{0}}
    \caption{\textsc{Comparison of Classification Techniques. (Arrhythmia data set)}}
      \vspace{-\baselineskip}
    \begin{tabular}{@{}lccccccl@{}}\toprule
    Method                    & Search (s) & acc                               & acc (normalized)             & acc (PCA-30)                   & acc (AE-30)\\ \midrule
    KNN-Brute-Force + DBSCAN  & $0.009$   & $76.6169 \pm \z{0}$                & $\bf{80.597 \pm 0}$          & $78 \pm \z{0}$                 & $\bf{80 \pm \z{0}}$\\
    KNN-ANNOY-BFS + DBSCAN    & $0.012$   & $76.6567 \pm \z{0.5340}$           & $\bf{80.597 \pm 0}$          & $\bf{78.16 \pm \z{0.7310}}$    & $\bf{80 \pm \z{0}}$\\
    SVM + DBSCAN              & $1.846$   & $76.6616 \pm \z{0}$                & $75.9219 \pm 0$              & $75 \pm \z{2}$                 & $75 \pm \z{4}$\\
    KNN-Brute-Force + kmeans  & $0.009$   & $76.6169 \pm \z{0}$                & $\bf{80.597 \pm 0}$          & $78 \pm \z{0}$                 & $\bf{80 \pm \z{0}}$\\
    KNN-ANNOY-BFS + kmeans    & $0.012$   & $76.6567 \pm \z{0}$                & $\bf{80.597 \pm 0}$          & $\bf{78.16 \pm \z{0.7310}}$    & $\bf{80 \pm \z{0}}$\\
    SVM + kmeans              & $1.846$   & $76.6616 \pm \z{0}$                & $75.9219 \pm 0$              & $75 \pm \z{2}$                 & $75 \pm \z{4}$\\
    \end{tabular}
    \label{table:Arrhythmia_result}
      \vspace{-\baselineskip}
  \end{table*}

  \begin{table*}[htb]
    \newcommand{\z}{\phantom{0}}
    \caption{\textsc{Comparison of Classification Techniques. (gene expression cancer RNA-Seq data set)}}
      \vspace{-\baselineskip}
    \begin{tabular}{@{}lccccccl@{}}\toprule
    Method                    & Search (s) & acc                               & acc (normalized)             & acc (PCA-30)                   & acc (AE-30)\\ \midrule
    KNN-Brute-Force + DBSCAN  & $0.009$   & $76.6169 \pm \z{0}$                & $\bf{80.597 \pm 0}$          & $78 \pm \z{0}$                 & $\bf{80 \pm \z{0}}$\\
    KNN-ANNOY-BFS + DBSCAN    & $0.012$   & $76.6567 \pm \z{0.5340}$           & $\bf{80.597 \pm 0}$          & $\bf{78.16 \pm \z{0.7310}}$    & $\bf{80 \pm \z{0}}$\\
    SVM + DBSCAN              & $1.846$   & $76.6616 \pm \z{4.0301}$           & $75.9219 \pm 2.736$          & $75 \pm \z{2}$                 & $75 \pm \z{4}$\\
    KNN-Brute-Force + kmeans  & $0.009$   & $76.6169 \pm \z{0}$                & $\bf{80.597 \pm 0}$          & $78 \pm \z{0}$                 & $\bf{80 \pm \z{0}}$\\
    KNN-ANNOY-BFS + kmeans    & $0.012$   & $76.6567 \pm \z{0.5340}$           & $\bf{80.597 \pm 0}$          & $\bf{78.16 \pm \z{0.7310}}$    & $\bf{80 \pm \z{0}}$\\
    SVM + kmeans              & $1.846$   & $76.6616 \pm \z{4.0301}$           & $75.9219 \pm 2.736$          & $75 \pm \z{2}$                 & $75 \pm \z{4}$\\
    \end{tabular}
    \label{table:gene_expression_result}
      \vspace{-\baselineskip}
  \end{table*}
